How to Analyze Build Logs --- A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-26 tse-paper/content.tex
status from before the meeting today

@@

To answer this question, we start our investigation---pictured in
\Cref{fig:overview}---with an
extensive literature study (step 1).
The literature
survey identifies various strategies to
analyze build logs, among which are developing
custom parsers, using regular expressions, doing manual inspections,
natural language processing, information retrieval, or searching
for keywords.
Unfortunately, our survey also shows that
less than half of the 61 works which rely on build log analysis
describe it in sufficient detail and that
% TODO Moritz: 14 is still quite big, it's 'impl available' when we saw
% no overlap.
Decide whether you want to keep this in :)
only 14 independent implementations are available, one of which stems
from the second author of this paper.
Out of these implementations, all are based on either a custom parser
or regular expressions.
%Using 1) a set of
% manually curated regular expressions,
% similar to TravisTorrent~\cite{beller2017oops},
% 2) information
% retrieval techniques,
% % Can you shortly explain the technique here?
% and 3) a list of search keywords
% to identify regions of interest in the build log.

@@

This lead us to the following research questions:
\begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ1:} What is the state-of-the-research on analyzing build logs?}
% TODO (resolved): All of these are passive
% it says resolved, but they still are?
% I exchanged 'extracted' with targeted / analysis
% 'information retrieved' or 'information extracted' will give us
% this is not IR neither IE discussions again
\begin{itemize}[leftmargin=1cm]
  \item[\textbf{RQ1.1:}] What information is targeted in build logs?
  \item[\textbf{RQ1.2:}] Which analysis techniques exist?
  \item[\textbf{RQ1.3:}] Which kinds of build logs are subject to
  analysis?
\end{itemize}
\end{simplebox}

@@

\section{Chunk Retrieval Techniques}
\label{sec:techniques}
%TODO here we sell our techniques as superior.
match in intro?
%TODO: really? currently the discussion does not show this 'need'!
The outcome of our literature survey shows the need for a new
generation of techniques to analyze build logs.
In this section we argue how our research sets the first step to
address this need by introducing three techniques that retrieve
specific substrings (chunks) from build logs.
We present defining characteristics of these so called \emph{chunk
retrieval techniques} and present the techniques we developed in
detail.
At the end we illustrate how the techniques operate on a concrete
example and sketch out their implementation.

@@

\subsection{The case for chunk retrieval on build logs}
% FIXME Caro
In summary, the results of the literature study show the need for
build log
analysis techniques that are \emph{automated},
\emph{build-environment agnostic}
and can be \emph{configured with little effort}.

@@

\subsection{Random Line Retrieval (RLR)}
\label{sec:expl-rlr}
% TODO: could you add two-three more references to the results of RLR in
% the discussion, to show how even seemingly low numbers are much better
% than RLR?
% TODO QUESTION: should I add those here? as references to the disc?
% or in the discussion? (you also already added some)
% In general: I think we talk a lot about RLR and it gets wordy.

@@

% TODO: these next two sections do not belong under this section --
%they are not a chunk retrieval technique.
%One way to fix it would be to rename the section.
% TODO QUESTION: Caro show whole structure
% -> introduction to crts, investigated techniques, ???

@@

% TODO -- this is a wrong title -- !!
% TODO find better one
\section{Empirical Comparison Study}

% TODO This section is not structured well.
%First, it misses an
% explanation of the bigger study design.
%Second, What is the difference between Study Process and
% Study Design? Third, the LogChunks section appears out of nowhere
% and is not related to the section title (different abstraction
% level).
%Perhaps a solution would be to be a bit inspired by this
% paper:
%https://inventitech.com/publications/2018_beller_spruit_spinellis_zaidman_on_the_dichotomy_of_debugging_behavior_among_programmers.pdf
% There is a research design section (which we are missing) and a
% Research Method section (which is a mixture of the current section
% titled Log Chunks and Study Process)

@@

% TODO: find better title!!!!
\subsection{Study Execution}
\Cref{fig:study} gives an overview over the steps within our empirical
comparison study.
In the following, we each of the steps and the metrics
we measure to answer our research quest

% TODO: I think you need to introduce a concept that makes clear what one
% ``folder'' consists of ...ions.

We apply every one of the four chunk retrieval techniques
% TODO Check abstraction level: leave out acronyms?
(PBE, CTS, KWS, and RLR) on all 80 repositories represented in
\emph{LogChunks} \circlenum{1}.
For each repository, we select training sets of size 1, 2, \dots 5
examples \circlenum{2}.
% For this, we select all examples in \emph{LogChunks}
% (as defined in \Cref{sec:logchunks})
% We begin by selecting all examples
% that correspond to one GitHub repository---and thus the
% same build environment (1).
We vary its size to measure how many examples we need to
confidently configure a technique.
The training set is so small because the examples have to be
manually created by a user.
A larger training set would oppose our goal of providing techniques
that can be configured with little effort
(see \Cref{sec:lit-sur:discussion}).
% TODO: The example? why only one?
The test set consists of an example based on the build log produced
chronologically after the build logs in the training set \circlenum{3}.
In this way, we train on examples from past build logs and test on
more recent logs.
% We chose a test set size of 1, as users of the techniques
% should receive reliable results on every build log they analyze.
% M: and why is this important? Doesn't everyone want such stability
%of results?
% C: motivation why only one test example.
% we can also leave that out
% and answer if we are asked about it
In the next step, we configure a chunk retrieval technique with
the examples from the training set \circlenum{4} and apply the technique
to the
training set \circlenum{5}, which produces the retrieval output
\circlenum{6}.
Based on this, we collect the following measurements \circlenum{7}:
the size of the training set (\textbf{RQ2.1}),
the number of structural categories in the training
set (\textbf{RQ2.2}),
the lines of the retrieval output ($\mathit{RetrievedLines}$),
and the oracle: the output defined in the test example
($\mathit{DesiredLines}$).
From these we calculate accuracy metrics (\textbf{RQ2.3}):

@@

	We define a successful retrieval as one where all desired
	lines were
	extracted, therefore when recall is one.
\end{itemize}

@@

\lstset{
  language=,
  morekeywords={Test, Output, Desired},
  keywordstyle=\textbf,
	frame=single
}
\begin{figure}[!t]
  \centering
  \begin{lstlisting}[breaklines=true]
Test Output:
Error: Invalid CSS after "2.3em": expected expression (e.g.
1px, bold), was ";"
	on line 86 of sass/components/dropdown.sass
Desired Test Output:
Error: Invalid CSS after "2.3em": expected expression (e.g.
1px, bold), was ";"
	on line 86 of sass/components/dropdown.sass
	from line 5 of sass/components/_all.sass
	from line 6 of bulma.sass
  \end{lstlisting}
  \caption{Example for an unsuccessful retrieval (PBE retrieved only
  two of the four targeted lines).}
  \label{lst:pbe-unsuccessful}
\end{figure}

@@

% TODO Say something about this being a pecularity of PBE ...
\Cref{fig:failure-reason-PBE} shows the results of chunk
retrieval with PBE.
Out of the overall 400 runs, 5 per each one of the 80 example
sets, PBE extracted all desired lines successfully in 138 cases.
In 59 cases, PBE could synthesize a regular expression program, though
it did not find match on the test build log.
In 30 cases, the synthesized program only extracted a
subset of the desired lines.
For these 30 cases, the average recall
was 28\%.
% TODO: Perhaps we should call it partially successful? Let's
% discuss this in a meeting
% TODO QUESTION: yes we can :)
\Cref{lst:pbe-unsuccessful} shows how an example of such
an \emph{unsuccessful retrieval} looks like.
In it, the synthesized program only
retrieved two of the four targeted lines.
In 173 of the 400 cases
could PROSE not synthesize a program consistent with all of the training
examples.

% TODO introudce this fig at large.
%Soemthing like: Zooming in
% on only the successful retrievals from (...), Fig ...
%shows ...

\Cref{fig:failure-reason-categorycount-PBE} shows the results of PBE
runs depend on the number of structural categories in the training and
test examples.
The figure demonstrates that program synthesis mostly
returns exactly the desired output when there is only one
structural category present in the training and test examples.
However, when
two or more structural categories are simultaneously present,
PROSE could in most cases not synthesize a program.
For four or more present
categories PROSE could never synthesize a consistent program.

\Cref{fig:recall-precision-examplecount-sythesisworked-PBE} shows
precision and recall of the 227 runs where PBE could synthesize a
program consistent with all training examples.
When the training set
size increases from one to two, recall, and F$_{1}$-score increase by
about 25\%, precision increases by about 10\%.
For two or more
training examples, recall, and F$_{1}$-score stay around 75\% and
precision around 96\%.

\subsection{Common Text Similarity (CTS)}
\label{sec:r:cts}
\begin{figure*}
\centering
    \textbf{Common Text Similarity (CTS)}\par\medskip
\begin{subfigure}[tb]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
		\caption{training set size.}
		\label{fig:recall-precision-examplecount-CTS}

\end{subfigure}\hspace{\fill}
\begin{subfigure}[tb]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
		\caption{structural category count
		in training and test set.}
		\label{fig:recall-precision-categorycount-CTS}
\end{subfigure}
\caption{Precision, recall, and F$_{1}$-score of chunk
retrieval with Common Text Similarity (CTS) compared by \ldots}
\end{figure*}

% TODO what about referencing the combined figure at first: something
%like shows the results of CTS on two beanplots of ...
%and ...., and then the subfigure
% TODO this goes for all techniques
% TODO QUESTION: yes, though then we have more redundant text
% that repeats everywhere and is already in the captions
% -> should we add it for the first time we include a type of figure?
% TODO Yes, that sounds good.
% FIXME CARO You might even say Figure 12-15 show two
% plots in the short text under the section heading.
% It just makes the
% text flow so much better.
\Cref{fig:recall-precision-examplecount-CTS} presents precision,
recall, and F$_{1}$-score of chunk retrieval using CTS for an
increasing number of training examples.
When using one to five
training examples, the size of the training set has no noticeable
influence on precision, recall or F$_{1}$-score of the chunk retrieval
with CTS.

\Cref{fig:recall-precision-categorycount-CTS} shows the same
measurements for an increasing number of structural categories in the
training and test examples.
With increasing category count, precision,
recall, and F$_{1}$-score decrease.
% Especially for more than four
% categories present we have no chunk retrieval runs where all desired
% lines were extracted.

\subsection{Keyword Search (KWS)}
\label{sec:r:kws}
\begin{figure*}
\centering
    \textbf{Keyword Search (KWS)}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
		\caption{training set size.}
		\label{fig:recall-precision-examplecount-KWS}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
		\caption{structural category count
		in training and test sets.}
		\label{fig:recall-precision-categorycount-KWS}
\end{subfigure}
\caption{Precision, recall, and F$_{1}$-score of chunk retrieval with
Keyword Search (KWS) compared by \ldots}
\end{figure*}

\Cref{fig:recall-precision-examplecount-KWS} presents precision,
recall, and F$_{1}$-score of chunk retrieval using KWS for different
numbers of training examples.
The recall increases by about 12\% when
increasing the size of the training set to more than one example,
while the precision stays constant at around 16\%.
The F$_{1}$-score
stays around 26\%.

@@

% TODO Perhaps, above in our section about logchunks, we would need some
% basic empirical stats -- e.g., how long are the files and how much
% do we usually extract from the log
\subsection{Random Line Retrieval}
\label{sec:r:rlr}

@@

\subsection{Comparison of All Techniques}
%TODO too short
% TODO CARO give outlook on results here
In this section, we aggregate and compare the results from
\Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr}.

% TODO CARO? check type of graph introduced
\Cref{fig:success-partial-all} compares the success of chunk
retrievals differentiated by techniques in our study.
% TODO It shows on the vertical axis the number of ?runs? ...
% and on the horizontal ...
CTS and KWS
extract at least some of the desired lines in 79\% and 88.5\%
of the chunk retrieval runs.
With 38.25\%, KWS also has the highest proportion of fully
successful extractions, followed by PBE with 34.5\%.
PBE has the
lowest number of partial retrievals with only 18 out of 400 chunk
retrieval runs.

\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all}
show the influence of all training and test examples being from the
same structural category compared to being multiple categories
For more
than one category being present, the recall of PBE decreases greatly.
% TODO this is not a meaningful comparsion to RLR.
%One would be to say that
% all of these techniques beat RLR handsdown -> discussion!
% TODO QUESTOIN: well they don't in this picture (PBE, multiple sc)
% maybe we can say that one figure earlier?
For CTS and KWS the values also decrease, while RLR is not affected by
the number of structural categories present.

@@

% TODO decision tree -> recommendation schema? You can use the more
%specific decision
% tree when referencing the figure.
For the interpretation of the study results, we look at each chunk
retrieval technique separately.
We give recommendations for
which types of log chunks and how many training examples
each technique is suited, as well as
how their output can be used further.
Following that, we discuss
which of these criteria should influence the decision to use a certain
chunk retrieval technique most.
Based on the empirical comparison, we present a
decision tree between the three techniques we investigated.

\subsection{Interpretation of Study Results}
% TODO CARO
%Begin the section by saying what you do in there
% Then at the end, say that you summarized it in Table 3 (or include
%Table 3
% in the discussion throughout the text.)
\Cref{tab:single-technique-recommendations} summarizes the
recommendations which we discuss
in this section.

@@

\noindent
\textbf{Configuration and Input.}
Our study results show that chunk retrieval with PBE gives best
results when the log chunks are structurally identical.
This is
because PROSE has difficulty synthesizing OR-based
programs~\cite{mayer2015user}.
PBE is thus suited to retrieve information
chunks that always have the same defining surrounding or internal
structure.
To extract for example the reason a build failed, the log
passage describing the failure would always have to start and
end the same way.

@@

\begin{figure}[tb]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/crt-recommendation.pdf}
		\caption{Our preliminary recommendation scheme for chunk
		retrieval techniques.}
		\label{fig:crt-recommendation}
\end{figure}

\subsection{Recommendation of Suitable Techniques}
% TODO CARO Make intro less generic?
After discussing the three chunk retrieval techniques separately we
now want to unify the results into one recommendation scheme.
% TODO Try to inductiviely let the figure emerge from the text, not this
% ``here is the figure; eat it''.
% C: ``How should I do this?''
% TODO CARO
% Already a better solution would be at the end of this section: We
% summarized these conditions in the decision tree in Fig ...
% also reference to the parts of the figure during the explanation
\Cref{fig:crt-recommendation} presents a decision tree
to answer the second research question;
If researchers or developers want to retrieve chunks from build logs,
they can follow the decision tree to identify the technique
suited best for their use case.
The decision tree is built up of questions
which either lead to more questions or to a leaf node containing a
recommended technique.

% TODO QUESTION
% shouldn't it also better be in threats to validity?
% it is as well.
%back for my thesis you said we should put it
% directly here to make it more prominent avoid angry critics
% I think it's good here
% but it's also self-contained so feel free to comment it out

% TODO we can't just have a paragraph in a scientific paper start with
% Caveat, I think ;-) Also, we should say why we THINK this is not
%the case.
% Otherwise we weaken our work unduly
\textbf{Caveat!}
This is a preliminary hypothesis based on the results
from our comparison study.
The recommendations could therefore be
influenced by idiosyncrasies of our specific implementation of the
chunk retrieval techniques as well as the \emph{LogChunks}
data set.

The first and most important aspect that influences a choice for
a chunk retrieval technique are the structural categories.
Are the targeted log chunks always presented in
the same structural way within the build logs? Then the information
chunks in all training examples and the analyzed build log are in the
same structural category.

If the information chunks are from multiple structural categories
and recall is more important than precision we recommend
to use KWS\@.
If precision is more important than recall, we
recommend CTS\@.
We also recommend CTS when the log chunks are
from one structural category, when the user does not require high
confidence in the precision or recall of the outcome and when one
would rather have output with low recall instead of no output at all.
When the representations are from one structural category and the user
wishes high confidence in the correctness of the output or prefers
no output over output with low recall, we recommend PBE\@.

@@

\subsection{Using the Recommendation Scheme}
% TODO QUESTION: which one do you mean here?
% TODO Perhaps add introduction from recommendation scheme here?

% TODO this is very nice again, perhaps a tiny bit on the trivial side.
% TODO CARO Do reference Figure 17 more, thoguh
To illustrate how one would use the decision tree to find a suitable
chunk retrieval technique we describe two concrete examples: a software
team
wanting to monitor their build performance and a
researcher investigating why builds fail.

In the first example, a software development team wants to monitor
the performance of the phases within their CI build.
They are using
Travis CI, which measures the duration of build phases and documents
this within the build log.
As all log statements that report timing
measurements are formatted the same way, the targeted log chunks are
from one structural category.
Therefore, the development team can use
PBE to retrieve the duration of a build phase.

In the second example, a researcher wants to investigate whether a small
or large group of test cases
causes build failures.
They gather
CI build logs from various projects.
The task of the researcher is to extract the names of the
failing test cases from each build log.
When they use our
recommendation scheme to select a chunk retrieval technique, they
first have to estimate how uniform the representation of the failing
test cases is in the investigated build logs.
As the researcher is
covering a wide range of test tools, the
log chunks they target are in various, non-predictable structural
representations.
The next question is whether they value precision
over recall.
As they have to manually inspect the results of both CTS
and KWS, they choose recall over precision to avoid having to inspect
the whole log in case the relevant information chunk was not
retrieved.
Therefore, the decision tree recommends the researcher to use KWS\@.

@@

\textbf{Training Set Size.}
Especially the results for CTS might be influenced by the fact that we
only trained on one to five examples.
We chose this small training set
size as a user has to provide the training examples
per repository or project.
We expect a developer or a researcher
to not want to provide more examples than the
small numbers we evaluated on.
% TODO maybe reference back to little effort technique in lit discus.
The fact that PBE and KWS performed best with already two training
examples shows that the training set size is large enough to
compare the three techniques.

>>>>

\tableofcontents

@@

To answer this question, we start our investigation---pictured in
\Cref{fig:overview}---with an
extensive literature study (step 1).
The literature
survey identifies various strategies to
analyze build logs, among which are developing
custom parsers, using regular expressions, doing manual inspections,
natural language processing, information retrieval, or searching
for keywords.
Unfortunately, our survey also shows that
less than half of the 61 works which rely on build log analysis
describe it in sufficient detail and that
% C: 14 is still quite big, it's 'impl available' when we saw
% no overlap.
Decide whether you want to keep this in :)
only 14 independent implementations are available, one of which stems
from the second author of this paper.
Out of these implementations, all are based on either a custom parser
or regular expressions.
%Using 1) a set of
% manually curated regular expressions,
% similar to TravisTorrent~\cite{beller2017oops},
% 2) information
% retrieval techniques,
% % Can you shortly explain the technique here?
% and 3) a list of search keywords
% to identify regions of interest in the build log.

@@

This lead us to the following research questions:
\begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ1:} What is the state-of-the-research on analyzing build logs?}
% M: All of these are passive
% C: it says resolved, but they still are?
% I exchanged 'extracted' with targeted / analysis
% 'information retrieved' or 'information extracted' will give us
% this is not IR neither IE discussions again
\begin{itemize}[leftmargin=1cm]
  \item[\textbf{RQ1.1:}] What information is targeted in build logs?
  \item[\textbf{RQ1.2:}] Which analysis techniques exist?
  \item[\textbf{RQ1.3:}] Which kinds of build logs are subject to
  analysis?
\end{itemize}
\end{simplebox}

@@

\section{Chunk Retrieval Techniques}
\label{sec:techniques}
%TODO here we sell our techniques as superior.
% match in intro?
%TODO: really? currently the discussion does not show this 'need'!
The outcome of our literature survey shows the need for a new
generation of techniques to analyze build logs.
In this section we argue how our research sets the first step to
address this need by introducing three techniques that retrieve
specific substrings (chunks) from build logs.
We present defining characteristics of these so called \emph{chunk
retrieval techniques} and present the techniques we developed in
detail.
At the end we illustrate how the techniques operate on a concrete
example and sketch out their implementation.

@@

\subsection{The Case for Chunk Retrieval on Build Logs}
In summary, the results of the literature study show the need for
build log
analysis techniques that are \emph{automated},
\emph{build-environment agnostic}
and can be \emph{configured with little effort}.

@@

\subsection{Random Line Retrieval (RLR)}
\label{sec:expl-rlr}

@@

@@

% TODO -- this is a wrong title -- !!
% find better one
\section{Empirical Comparison Study}

%Second, What is the difference between Study Process and
% Study Design? Third, the LogChunks section appears out of nowhere
% and is not related to the section title (different abstraction
% level).

@@

% TODO: find better title!!!!
\subsection{Study Execution}
\Cref{fig:study} gives an overview over the steps within our empirical
comparison study.
In the following, we each of the steps and the metrics
we measure to answer our research questions.

We apply every one of the four chunk retrieval techniques
% TODO Check abstraction level: leave out acronyms?
(PBE, CTS, KWS, and RLR) on all 80 repositories represented in
\emph{LogChunks} \circlenum{1}.
For each repository, we select training sets of size 1, 2, \dots 5
examples \circlenum{2}.
% For this, we select all examples in \emph{LogChunks}
% (as defined in \Cref{sec:logchunks})
% We begin by selecting all examples
% that correspond to one GitHub repository---and thus the
% same build environment (1).
We vary its size to measure how many examples we need to
confidently configure a technique.
The training set is so small because the examples have to be
manually created by a user.
A larger training set would oppose our goal of providing techniques
that can be configured with little effort
(see \Cref{sec:lit-sur:discussion}).
The test set consists of an example based on the build log produced
chronologically after the build logs in the training set \circlenum{3}.
In this way, we train on examples from past build logs and test on
more recent logs.
% We chose a test set size of 1, as users of the techniques
% should receive reliable results on every build log they analyze.
% M: and why is this important? Doesn't everyone want such stability
%of results?
% C: motivation why only one test example.
% we can also leave that out
% and answer if we are asked about it
In the next step, we configure a chunk retrieval technique with
the examples from the training set \circlenum{4} and apply the technique
to the
training set \circlenum{5}, which produces the retrieval output
\circlenum{6}.
Based on this, we collect the following measurements \circlenum{7}:
the size of the training set (\textbf{RQ2.1}),
the number of structural categories in the training
set (\textbf{RQ2.2}),
the lines of the retrieval output ($\mathit{RetrievedLines}$),
and the oracle: the output defined in the test example
($\mathit{DesiredLines}$).
From these we calculate accuracy metrics (\textbf{RQ2.3}):

@@

	We define a successful retrieval as one where all desired
	lines were extracted, therefore when recall is one.
  % TODO introduce partially successful and (new) unsuccessful
\end{itemize}

@@

\lstset{
  language=,
  morekeywords={Test, Output, Desired},
  keywordstyle=\textbf,
	frame=single
}
\begin{figure}[!t]
  \centering
  \begin{lstlisting}[breaklines=true]
Test Output:
Error: Invalid CSS after "2.3em": expected expression (e.g.
1px, bold), was ";"
	on line 86 of sass/components/dropdown.sass
Desired Test Output:
Error: Invalid CSS after "2.3em": expected expression (e.g.
1px, bold), was ";"
	on line 86 of sass/components/dropdown.sass
	from line 5 of sass/components/_all.sass
	from line 6 of bulma.sass
  \end{lstlisting}
  \caption{Example for a partially successful retrieval
  (PBE retrieved only
  two of the four targeted lines).}
  \label{lst:pbe-unsuccessful}
\end{figure}

@@

% actually, we could cut this figure and move it's explanation
% to the next one (this is an aggregation of the next one)
% however, having them separate eases the entry into the results a bit
% and we have explanation of the categories before the more complicated
% aspect of the change with more structural categories
\Cref{fig:failure-reason-PBE} shows the results of chunk
retrieval with PBE.
It shows how many of the retrieval runs were successful or
partially successful, as well as the number of runs where the
synthesized program did not match on the analyzed build log or where
no program could be synthesized.
% The last two results stem from the regular expressions and their
% synthesis, therefore only apply to PBE.
Out of the overall 400 runs, 5 per each one of the 80 example
sets, PBE extracted all desired lines successfully in 138 cases.
In 59 cases, PBE could synthesize a regular expression program, though
it did not match on the test build log.
In 30 cases, the synthesized program only extracted a
subset of the desired lines.
For these 30 cases, the average recall
was 28\%.
\Cref{lst:pbe-unsuccessful} shows how an example of such
an \emph{partially successful retrieval} looks like.
In it, the synthesized program only
retrieved two of the four targeted lines.
In 173 of the 400 cases
could PROSE not synthesize a program consistent with all of the training
examples.

\Cref{fig:failure-reason-categorycount-PBE} shows how
the results of PBE
runs depend on the number of structural categories in the training and
test examples.
% It shows the categories from above change depending on how many
% structural categories are present.
The figure demonstrates that program synthesis mostly
returns exactly the desired output when there is only one
structural category present in the training and test examples.
However, when
two or more structural categories are simultaneously present,
PROSE could in most cases not synthesize a program.
For four or more present
categories PROSE could never synthesize a consistent program.

Zooming in on only the 227 runs where PBE could synthesize a program,
\Cref{fig:recall-precision-examplecount-sythesisworked-PBE}
presents violin plots of the precision, the recall
and the F$_{1}$-score
of these runs compared with the number of examples in the training set.
The black horizontal lines show the average of these measurements.
When the training set
size increases from one to two, recall, and F$_{1}$-score increase by
about 25\%, precision increases by about 10\%.
For two or more
training examples, recall, and F$_{1}$-score stay around 75\% and
precision around 96\%.

\subsection{Common Text Similarity (CTS)}
\label{sec:r:cts}

\begin{figure*}
\centering
    \textbf{Common Text Similarity (CTS)}\par\medskip
\begin{subfigure}[tb]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
		\caption{training set size.}
		\label{fig:recall-precision-examplecount-CTS}

\end{subfigure}\hspace{\fill}
\begin{subfigure}[tb]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
		\caption{structural category count
		in training and test set.}
		\label{fig:recall-precision-categorycount-CTS}
\end{subfigure}
\caption{Precision, recall, and F$_{1}$-score of chunk
retrieval with Common Text Similarity (CTS) compared by \ldots}
\label{fig:results-CTS}
\end{figure*}

% You might even say Figure 12-15 show two
% plots in the short text under the section heading.
% It just makes the
% text flow so much better.

% The following sections are each quite short...
% we could merge them, but then it loses consistency with the other
% result subsections where each plot gets an own paragraph

\Cref{fig:results-CTS} shows violin plots
of the precision,
recall, and F$_{1}$-score of the chunk retrieval runs with CTS.
%The black horizontal lines show the average of these measurements.

\Cref{fig:recall-precision-examplecount-CTS} presents the
measurements for an
increasing number of training examples.
When using one to five
training examples, the size of the training set has no noticeable
influence on precision, recall or F$_{1}$-score of the chunk retrieval
with CTS.

\Cref{fig:recall-precision-categorycount-CTS} shows the
measurements for an increasing number of structural categories in the
training and test examples.
With increasing category count, precision,
recall, and F$_{1}$-score decrease.
% Especially for more than four
% categories present we have no chunk retrieval runs where all desired
% lines were extracted.

\subsection{Keyword Search (KWS)}
\label{sec:r:kws}
\begin{figure*}
\centering
    \textbf{Keyword Search (KWS)}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
		\caption{training set size.}
		\label{fig:recall-precision-examplecount-KWS}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
		\caption{structural category count
		in training and test sets.}
		\label{fig:recall-precision-categorycount-KWS}
\end{subfigure}
\caption{Precision, recall, and F$_{1}$-score of chunk retrieval with
Keyword Search (KWS) compared by \ldots}
\label{fig:results-KWS}
\end{figure*}

\Cref{fig:results-KWS} shows violin plots
of the precision,
recall, and F$_{1}$-score of the chunk retrieval runs with KWS.
%The black horizontal lines show the average of these measurements.

\Cref{fig:recall-precision-examplecount-KWS} presents these
measurements for different
numbers of training examples.
The recall increases by about 12\% when
increasing the size of the training set to more than one example,
while the precision stays constant at around 16\%.
The F$_{1}$-score
stays around 26\%.

@@

% M: Perhaps, above in our section about logchunks, we would need some
% basic empirical stats -- e.g., how long are the files and how much
% do we usually extract from the log
% C: yup, that would be nice
% sadly, it's quite a bit of work to get those :/
% maybe I/We'll do it at the end
\subsection{Random Line Retrieval}
\label{sec:r:rlr}

@@

\subsection{Comparison of All Techniques}
In this section, we compare the results of all four chunk retrieval
techniques and show the impact of structural categories on precision,
recall and F$_{1}$-scores of the different techniques.

% absolute results? is there a nice word for these results
\Cref{fig:success-partial-all} compares the results all of chunk
retrievals techniques in our study.
It shows how many runs per technique were successful, partially
successful or unsuccessful in retrieving the chunk defined in the
test example.
CTS and KWS
extract at least some of the desired lines in 79\% and 88.5\%
of the chunk retrieval runs.
With 38.25\%, KWS also has the highest proportion of fully
successful extractions, followed by PBE with 34.5\%.
PBE has the
lowest number of partial retrievals with only 18 out of 400 chunk
retrieval runs.
All techniques clearly outperform the random baseline (RLR).

\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all}
show the influence of all training and test examples being from the
same structural category compared to being multiple categories
For more
than one category being present, the recall of PBE decreases greatly.
For CTS and KWS the values also decrease, while RLR is not affected by
the number of structural categories present.
Again, all techniques---except for PBE with multiple structural
categories---yield better retrievals than RLR.

@@

For the interpretation of the study results, we look at each chunk
retrieval technique separately.
Next, we discuss
which criteria should influence the decision to use a certain
chunk retrieval technique most.
Based on the empirical comparison, we present a
decision tree between the three techniques we investigated.

\subsection{Interpretation of Study Results}
Following from the results of the empirical study,
we give recommendations for
which types of log chunks and how many training examples
each technique is suited, as well as
how their output can be used further.
We summarize these recommendations in
\Cref{tab:single-technique-recommendations}.

@@

\noindent
\textbf{Configuration and Input.}
The study results show that chunk retrieval with PBE gives best
results when the log chunks are structurally identical.
This is
because PROSE has difficulty synthesizing OR-based
programs~\cite{mayer2015user}.
PBE is thus suited to retrieve information
chunks that always have the same defining surrounding or internal
structure.
To extract for example the reason a build failed, the log
passage describing the failure would always have to start and
end the same way.

@@

\begin{figure}[tb]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/crt-recommendation.pdf}
		\caption{Our decision tree for chunk
		retrieval techniques.}
		\label{fig:crt-recommendation}
\end{figure}

\subsection{Recommendation of Suitable Techniques}
We saw, that each of the techniques is suited for different types of
log chunks and the output of each is suited for different uses.
Now, we unify these results into conditions to answer
our second research questions;
If researchers or developers want to retrieve chunks from build logs,
they can follow these conditions to identify the technique
suited best for their use case.
% I want to ref the figure early bc I believe the text is easier
% to follow when looking at the figure as well
We summarize these conditions in the decision tree in
\Cref{fig:crt-recommendation}.
It is built up of questions
which either lead to more questions or to a leaf node containing a
recommended technique.
At the end of this section we give two concrete examples on how to
apply our decision tree.

% we can't just have a paragraph in a scientific paper start with
% Caveat, I think ;-) Also, we should say why we THINK this is not
%the case.
% Otherwise we weaken our work unduly
% Of course we can! xD
% Agree with the rest.
It's in TtV, quite close actually
% so I'll comment this out
% also #moreselling :D
% \textbf{Caveat!}
% This is a preliminary hypothesis based on the results
% from our comparison study.
% The recommendations could therefore be
% influenced by idiosyncrasies of our specific implementation of the
% chunk retrieval techniques as well as the \emph{LogChunks}
% data set.

The first and most important aspect that influences a choice for
a chunk retrieval technique are the structural categories.
Are the targeted log chunks always presented in
the same structural way within the build logs? Then the information
chunks in all training examples and the analyzed build log are in the
same structural category.
This is why the first question in \Cref{fig:crt-recommendation} asks
how many structural categories the targeted log chunks have.

If the information chunks are from multiple structural categories
and recall is more important than precision we recommend
to use KWS\@.
If precision is more important than recall, we
recommend CTS, as \Cref{fig:crt-recommendation} shows on the
right half of the decision tree.
We also recommend CTS when the log chunks are
from one structural category, when the user does not require high
confidence in the precision or recall of the outcome and when one
would rather have output with low recall instead of no output at all.
On the leftmost path of the decision tree,
when the representations are from one structural category and the user
wishes high confidence in the correctness of the output or prefers
no output over output with low recall, we recommend PBE\@.

@@

\subsection{Using the Decision Tree}
To illustrate how one would use the decision tree to find a suitable
chunk retrieval technique we describe two concrete examples: a software
team
wanting to monitor their build performance and a
researcher investigating why builds fail.

In the first example, a software development team wants to monitor
the performance of the phases within their CI build.
They are using
Travis CI, which measures the duration of build phases and documents
this within the build log.
As all log statements that report timing
measurements are formatted the same way, the targeted log chunks are
from one structural category.
Therefore, following the leftmost path in
\Cref{fig:crt-recommendation},
the development team should use
PBE to retrieve the duration of a build phase.

In the second example, a researcher wants to investigate whether a small
or large group of test cases
causes build failures.
They gather
CI build logs from various projects.
The task of the researcher is to extract the names of the
failing test cases from each build log.
When they use the
decision tree to select a chunk retrieval technique, they
first have to estimate how uniform the representation of the failing
test cases is in the investigated build logs.
As the researcher is
covering a wide range of test tools, the
log chunks they target are in various, non-predictable structural
representations.
The next question is whether they value precision
over recall.
As they have to manually inspect the results of both CTS
and KWS, they choose recall over precision to avoid having to inspect
the whole log in case the relevant information chunk was not
retrieved.
Therefore, following the rightmost path in
\Cref{fig:crt-recommendation},
the decision tree recommends the researcher to use KWS\@.

@@

\textbf{Training Set Size.}
Especially the results for CTS might be influenced by the fact that we
only trained on one to five examples.
We chose this small training set
size as a user has to provide the training examples
per repository or project and one of the central aims of the chunk
retrieval techniques is that they can be set up wit little effort.
The fact that PBE and KWS performed best with already two training
examples shows that the training set size is large enough to
compare the three techniques.
